Union and intersection contracts are hard, actually

### 2021-06-09 paper.tex
Modify my bit for consistent terminology: values satisfy a contract

Like for static types, a valid value for the contract \nickel{A @| B}
is a value which is valid either for contract \nickel{A} or for
contract \nickel{B} (though in Section~\ref{sec:issues-literature} we
will see that it may be desirable to weaken this definition).

@@

An intersection type \nickel{A @& B} validates values which are both
valid for contract \nickel{A} and contract \nickel{B}.

@@

For higher-order contracts, the notion has two facets. A \nickel{Num -> Str}
contract can be violated in two ways: by the function returning a value that is
not a string, or by the caller providing an argument that is not a number.  The
former is embodied by the same notion as before: $f \in \llbracket Num \to Str
\rrbracket^+$ if whenever $f$ receives a number, it returns a string.  One
important contribution of~\cite{KeilThiemannUnionIntersection}, upon
which~\cite{RootCauseOfBlame} builds upon, is to extend the notion of contract
satisfaction to \emph{contexts}, embodying the caller's
obligations. A context $K$ is a term with a hole to be filled with a term (see
Figure~\ref{fig:valid-contexts} for examples). Then, $K \in \llbracket Num \to
Str \rrbracket^-$ (the context $K$ satisfies the contract \nickel{Num -> Str})
if it only applies the hole to arguments satisfying the \nickel{Num} contract.

>>>>

Like for static types, value which satisfies the contract \nickel{A @| B}
is a value which satisfy either contract \nickel{A} or
contract \nickel{B} (though in Section~\ref{sec:issues-literature} we
will see that it may be desirable to weaken this definition).

@@

An intersection type \nickel{A @& B} is satisfied by values which
satisfy both contract \nickel{A} and contract \nickel{B}.

@@

For higher-order contracts, the notion has two facets. A \nickel{Num -> Str}
contract can be violated in two ways: by the function returning a value that is
not a string, or by the caller providing an argument that is not a number.  The
former is embodied by the same notion as before: $f \in \llbracket Num \to Str
\rrbracket^+$ if whenever $f$ receives a number, it returns a string.  One
important contribution of~\cite{KeilThiemannUnionIntersection}, upon
which~\cite{RootCauseOfBlame} builds upon, is to extend the notion of contract
satisfaction to \emph{contexts}, embodying the caller's
obligations. A context $K$ is a term with a hole to be filled with a term (Figure~\ref{fig:valid-contexts} has examples). Then, $K \in \llbracket Num \to
Str \rrbracket^-$ (the context $K$ satisfies the contract \nickel{Num -> Str})
if it only applies the hole to arguments satisfying the \nickel{Num} contract.
